%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{float}
\usepackage{graphicx}% Include figure files
%\usepackage{cite}
%\usepackage{rotating}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{tabularx}
\usepackage{hyperref}
%\usepackage{mciteplus}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multirow}
%\usepackage{multicol}
%\usepackage{booktabs}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{sidecap}   % sidecaptions
\usepackage{subfigure}
\usepackage{ulem} % strikeout
\usepackage{array}
\usepackage{xcolor}
\usepackage[titletoc]{appendix}
\usepackage{rotating}
\usepackage{lipsum}  
%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{bm}
\MakeOuterQuote{"}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\textwidth}{18.0cm}
\setlength{\textheight}{23.0cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\topmargin}{0.0cm}
\setlength{\footskip}{1.5cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.3}
%\usepackage[style=numeric-comp,sorting=none]{biblatex}%<- specify style
%\addbibresource{ref.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\baselineskip 0.7cm
\title{\bf \color{blue}Title }
\vskip 3cm
\author{Partner A Name \\ (Partner A Roll No) \and 
Partner B Name \\ (Partner B Roll No) \and 
Partner C Name \\ (Partner C Roll N0) \\
{\color{blue}S.G.T.B. Khalsa College, University of
Delhi, Delhi-110007, India.} }

\maketitle
\vskip 4cm
\begin{center}
{\it {\color{blue}Project Report Submitted to}}\\
Dr. Mamta and Dr. H. C. Ramo \\
\textit{\color{blue}as part of internal assessment for the course}\\
 "32223902 - Computational Physics Skills"
\end{center}

\pagenumbering{gobble}

\newpage
%\vskip 1cm

\pagenumbering{roman}
\abstract{Abstract should be 100-150 words}
%\abstract{\lipsum[1-1]}
\newpage
\tableofcontents
\newpage

\pagenumbering{arabic}
\section{Introduction}
\label{sec:intro}
\begin{itemize}
    \item Total length 1-2 pages
    \item Introduce the topic - include Motivation for choosing the topic 
    \item Last paragraph should contain plan of the report -
one sentence about each of the following sections
\end{itemize}

Cite a paper as\cite{PhysRev.47.777}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theory}
\label{sec:theory}
\begin{itemize}
    \item Clear statement of the physics problem.
    \item Mathematical Modeling : Convert the physics problem into a dimensionless mathematics problem.
    \item Include all relevant equations explaining each symbol -- No derivation required. If any proof or derivation is to be given, include it in an appendix.
    \item You may include some figures (Proper citation required) or circuits.
    \item Any exact analytical results if available should be also included.
    \item cite the relevant references.
    \item Length of this section should be 2-4 pages.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
\label{sec:method}
\begin{itemize}
    \item List the Tools and numerical methods used
    \item Algorithms of the numerical methods used -- use the package for the algorithm.
    \item Also list the inbuilt functions of scipy (if any) used to compare your results
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis of Numerical Results}
Include all graphs, tables and analysis of the results. This should be a detailed section. There is no restriction of length here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{sec:summary}
\begin{itemize}
    \item This section contains summary of your results or conclusions
    \item It should also include our experience and what you have learnt in this project
    \item Length should be 300- 500 words 
\end{itemize}

\bibliography{ref} % the file ref.bib contains all references in bibtex style
\bibliographystyle{ieeetr}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\appendix
\section{Programs}
Include your fortran/python programs and gnuplot scripts in this section: 
Use the listings package.
\newpage 
\section{Contribution of team mates}
\large{\bf {Contribution of "{\it name of partner A}"}}
\begin{itemize}
   \item In Formulation of the problem:  
   \item  In Programming: 
   \item  In Plotting Graphs:
   \item  In Report Writing: 
\end{itemize}
\large{\bf {Contribution of "{\it name of partner B}"}}
\begin{itemize}
   \item In Formulation of the problem:  
   \item  In Programming: 
   \item  In Plotting Graphs:
   \item  In Report Writing:
\end{itemize}
\large{\bf {Contribution of "{\it name of partner C}"}}
\begin{itemize}
   \item In Formulation of the problem:  
   \item  In Programming: 
   \item  In Plotting Graphs:
   \item  In Report Writing: 
\end{itemize}

%%%
\end{document}
